---
title: "Tetanus infection dashboard"
output:
  flexdashboard::flex_dashboard:
    social: menu
    vertical_layout: fill
    theme: yeti
  html_document:
    df_print: paged
---

``` {js}
// Inverse the color of navigation bar.
$('.navbar-inverse').removeClass('navbar-inverse').addClass('navbar-default');
```


```{r setup, include=FALSE}
library(flexdashboard) 
library(highcharter) 
library(viridis) 
library(tidyverse) 
library(countrycode) 
library(crosstalk) 
library(plotly) 
```

```{r include=FALSE}
#setup warna palet
tropical_six <- list(
  "prussian blue"    = "#103851",
  "hunter green"     = "#316A4F",
  "satin sheen gold" = "#BAA147",
  "caramel"          = "#BE7E54",
  "cadet gray"       = "#8499AA",
  "caput mortuum"    = "#592822"
)

tropical_pal <- function(
    primary = "prussian blue",
    other = "cadet gray",
    direction = 1
) {
  stopifnot(primary %in% names(tropical_six))
  
  function(n) {
    if (n > 6) warning("Tropical Color Palette only has 6 colors cok.")
    
    if (n == 2) {
      other <- if (!other %in% names(tropical_six)) {
        other
      } else {
        tropical_six[other]
      }
      color_list <- c(other, tropical_six[primary])
    } else {
      color_list <- tropical_six[1:n]
    }
    
    color_list <- unname(unlist(color_list))
    if (direction >= 0) color_list else rev(color_list)
  }
}

scale_fill_tropical <- function(
    primary = "prussian blue",
    other = "cadet gray",
    direction = 1,
    ...
) {
  ggplot2::discrete_scale(
    "fill", "tropical",
    tropical_pal(primary, other, direction),
    ...
  )
}



#### 

data1 <- read.csv("/Users/edodanilyan/Documents/R project/dashboard/number-of-deaths-from-tetanus.csv")
data11 <- data1 %>%
  select(Year, Deaths) %>%
  group_by(Year) %>%
  summarise(Deaths = round((sum(Deaths))), 2)
##
country_tibble1 <- data1 %>%
  select(Entity, Deaths) %>%
  filter(Entity != 'African Region (WHO)',
         Entity != 'East Asia & Pacific (WB)',
         Entity != 'Eastern Mediterranean Region (WHO)',
         Entity != 'Europe & Central Asia (WB)',
         Entity != 'European Region (WHO)',
         Entity != 'G20',
         Entity != 'Latin America & Caribbean (WB)',
         Entity != 'Middle East & North Africa (WB)',
         Entity != 'North America (WB)',
         Entity != 'OECD Countries',
         Entity != 'Region of the Americas (WHO)',
         Entity != 'South Asia (WB)',
         Entity != 'South-East Asia Region (WHO)',
         Entity != 'Sub-Saharan Africa (WB)',
         Entity != 'Western Pacific Region (WHO)',
         Entity != 'World Bank High Income',
         Entity != 'World Bank Low Income',
         Entity != 'World Bank Lower Middle Income',
         Entity != 'World Bank Upper Middle Income',
         Entity != 'World')%>%
  group_by(Entity) %>%
  summarize(Deaths = round((sum(Deaths))), 2) 
##
data2 <- read.csv("/Users/edodanilyan/Documents/R project/dashboard/tetanus-deaths-by-age-group.csv")
data2 <- data2 %>% rename('<5' = 'X.5', 
                 '>70' = 'X.70', 
                 '50-69'='X50.69' , 
                 '15-49'= 'X15.49' , 
                 '5-14'='X5.14' ) %>%
  pivot_longer(cols=c('<5', '>70', '50-69', '15-49', '5-14'),
                    names_to='age_group',
                    values_to='deaths')
data2$age_group  <- factor(data2$age_group, levels=c('<5','5-14','15-49', '50-69', '>70'))

age_tibble1 <- data2 %>%
  group_by(Year, age_group) %>%
  summarise(deaths = round((sum(deaths))))
age_tibble1$age_group  <- factor(age_tibble1$age_group, levels=c('<5','5-14','15-49', '50-69', '>70'))
# Pick color for graph. 
age_color <- rev(plasma(5))

country_bar1 <- data1 %>%
  filter(Entity != 'African Region (WHO)',
         Entity != 'East Asia & Pacific (WB)',
         Entity != 'Eastern Mediterranean Region (WHO)',
         Entity != 'Europe & Central Asia (WB)',
         Entity != 'European Region (WHO)',
         Entity != 'G20',
         Entity != 'Latin America & Caribbean (WB)',
         Entity != 'Middle East & North Africa (WB)',
         Entity != 'North America (WB)',
         Entity != 'OECD Countries',
         Entity != 'Region of the Americas (WHO)',
         Entity != 'South Asia (WB)',
         Entity != 'South-East Asia Region (WHO)',
         Entity != 'Sub-Saharan Africa (WB)',
         Entity != 'Western Pacific Region (WHO)',
         Entity != 'World Bank High Income',
         Entity != 'World Bank Low Income',
         Entity != 'World Bank Lower Middle Income',
         Entity != 'World Bank Upper Middle Income',
         Entity != 'World')%>%
  group_by(Entity) %>%
  summarise(deaths = round((sum(Deaths)))) %>%
  arrange(desc(deaths))
```

<style>
.colored {
  background-color: #FAFAFA;
}
</style>


Worldwide
=======================================================================

Column {.tabset .tabset-fade data-width=700 .colored }
-----------------------------------------------------------------------

### Worldwide deaths from tetanus infection {.no-padding}

```{r}
highchart() %>% 
  hc_add_series(data11, hcaes(x = Year, y = Deaths), type = "line") %>%
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5, headerFormat = "", pointFormat = paste("Year: <b>{point.x}</b> <br> Deaths: <b>{point.y}</b>")) %>%
  hc_title(text = "Worldwide cases of death from tetanus") %>% 
  hc_subtitle(text = "1990-2019") %>%
  hc_colorAxis(minColor = "yellow", maxColor = "#592822") %>%
  hc_xAxis(title = list(text = "Year")) %>%
  hc_yAxis(title = list(text = "Deaths"),
           allowDecimals = FALSE,
           plotLines = list(list(
             color = "black", width = 1, dashStyle = "Dash", 
             value = mean(data11$Deaths),
             label = list(text = "Mean = 667745.9", 
                          style = list(color = "black"))))) %>%
  hc_legend(enabled = FALSE) 
```


### Worldwide deaths from tetanus infection by age {.no-padding}

```{r}
highchart() %>% 
  hc_add_series(age_tibble1, hcaes(x = Year, y = deaths, group = age_group), type = "line", color = age_color) %>%
  hc_tooltip(crosshairs = TRUE, borderWidth = 1.5, headerFormat = "", pointFormat = paste("Year: <b>{point.x}</b> <br>","Age: <b>{point.age_group}</b><br>", "Deaths: <b>{point.y}</b>")) %>%
  hc_title(text = "Worldwide deaths from tetanus infection by age") %>% 
  hc_subtitle(text = "1990-2019") %>%
  hc_xAxis(title = list(text = "Year")) %>%
  hc_yAxis(title = list(text = "Deaths"),
           allowDecimals = FALSE,
           plotLines = list(list(
             color = "black", width = 1, dashStyle = "Dash",
             value = mean(data11$Deaths),
             label = list(text = "Mean = 667745.9", 
                          style = list(color = 'black'))))) %>%
  hc_legend(element_blank())
```
Column {data-width=300}
-----------------------------------------------------------------------

### Total deaths <font size='1'> (1990-2019) </font>
```{r}

total_deaths <- round(sum(data11$Deaths), 2)

valueBox(total_deaths, icon = "fa-plus", color = '#592822')
```
### Worldwide deaths by age {.no-title .no-padding .colored }
```{r}
pie_age1 <- data2 %>%
  group_by(age_group) %>%
  summarise(deaths = round((sum(deaths)))) %>%
  arrange(deaths)
pie_age1$age_group  <- factor(pie_age1$age_group, levels=c('<5','5-14','15-49', '50-69', '>70'))
highchart() %>% 
  hc_add_series(pie_age1, hcaes(x = age_group, y = deaths, 
                               color = age_color), type = "pie") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", pointFormat = paste("Age: <b>{point.age_group} ({point.percentage:.1f}%)</b> <br> Deaths: <b>{point.y}</b>")) %>% 
  hc_title(text = "Worldwide deaths by age") %>% 
  hc_subtitle(text = "1990-2019") %>%
  hc_plotOptions(pie = list(dataLabels = list(distance = 15, 
                                              style = list(fontSize = 10)), 
                            size = 180))
```

Country
=======================================================================

Column {.tabset .tabset-fade data-width=700 .colored }
-----------------------------------------------------------------------
### Deaths by country and age
```{r}
country_bar_age1 <- data2 %>%
  drop_na() %>%
  filter(Entity != 'African Region (WHO)',
         Entity != 'East Asia & Pacific (WB)',
         Entity != 'Eastern Mediterranean Region (WHO)',
         Entity != 'Europe & Central Asia (WB)',
         Entity != 'European Region (WHO)',
         Entity != 'G20',
         Entity != 'Latin America & Caribbean (WB)',
         Entity != 'Middle East & North Africa (WB)',
         Entity != 'North America (WB)',
         Entity != 'OECD Countries',
         Entity != 'Region of the Americas (WHO)',
         Entity != 'South Asia (WB)',
         Entity != 'South-East Asia Region (WHO)',
         Entity != 'Sub-Saharan Africa (WB)',
         Entity != 'Western Pacific Region (WHO)',
         Entity != 'World Bank High Income',
         Entity != 'World Bank Low Income',
         Entity != 'World Bank Lower Middle Income',
         Entity != 'World Bank Upper Middle Income',
         Entity != 'World')%>%
  group_by(Entity, age_group) %>%
  summarise(deaths = round((sum(deaths))))
country_bar_age1$age_group  <- factor(country_bar_age1$age_group, levels=c('<5','5-14','15-49', '50-69', '>70'))
# Create interactive bar plot.
highchart() %>%
  hc_add_series(country_bar_age1, hcaes(x = Entity, y = deaths, group = age_group), type = "bar", color = age_color)  %>% 
  hc_tooltip(borderWidth = 1.5, pointFormat = paste("Age: <b>{point.age} ({point.percentage:.1f}%)</b> <br> Deaths: <b>{point.y}</b>")) %>%
  hc_title(text = "Deaths by country and age") %>% 
  hc_subtitle(text = "1990-2019") %>%
  hc_xAxis(categories = country_tibble1$Entity,
           labels = list(step = 1),
           min = 0, max = 30,
           scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Percent of total suicides")) %>%
  hc_plotOptions(bar = list(stacking = "percent", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5))
```
Column {.tabset .tabset-fade data-width=700 .colored }
-----------------------------------------------------------------------
### Map {.no-title .no-padding}
```{r}
highchart() %>%
  hc_add_series_map(worldgeojson, country_tibble1, value = "Deaths", 
                    joinBy = c('name','Entity'))  %>% 
  # hc_colors(cols) %>%
  # hc_colorAxis(dataClasses = color_classes(c(seq(0, 1500000, by = 250000)))) %>% 
  hc_colorAxis(stops = color_stops(8, c("#fee08b","#cc0000"))) %>% 
  hc_title(text = "Deaths from tetanus by country") %>% 
  hc_subtitle(text = "1990-2019") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", valueSuffix = " deaths")


```

### Barchart {.no-title .no-padding}
```{r}
highchart() %>%
  hc_add_series(country_bar1, hcaes(x = Entity, y = deaths), type = "bar")  %>%
  hc_colorAxis(stops = color_stops(8, c("#fee08b","#cc0000"))) %>% 
  hc_tooltip(borderWidth = 1.5, 
             pointFormat = paste("Reported deaths: <b>{point.y}</b>")) %>%
  hc_legend(enabled = FALSE) %>%
  hc_title(text = "Deaths by country") %>% 
  hc_subtitle(text = "1990-2019") %>% 
  hc_xAxis(
  categories = country_bar1$Entity, labels = list(step = 1),
       min = 0, max = 30,
        scrollbar = list(enabled = TRUE)) %>%
  hc_yAxis(title = list(text = "Deaths")) %>%
  hc_plotOptions(bar = list(stacking = "normal", 
                            pointPadding = 0, groupPadding = 0, borderWidth = 0.5))
```

About {data-icon="fa-info-circle"}
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### { .colored }

**Author information:**

To see my data visualization portfolio, please visit:

https://edodanilyan.com 

Column {data-width=500}
-----------------------------------------------------------------------

### { .colored }

**References:**  

The data set used to create the dashboard can be found at:   
https://ourworldindata.org/tetanus